Plug-and-play dual-tree algorithm runtime analysis

### 2015-08-14 bounds-files/general-runtime-bound.tex
Refactor for similar notation in theorem/lemma statements.

\begin{lemma}
\label{lem:extcase1}
For a dual-tree algorithm with $S_q \sim S_r \sim O(N)$ using cover trees and
the traversal given in Algorithm \ref{alg:cover-tree-dual}, the number of extra
reference recursions that happen before the first query recursion is bounded by

@@

\begin{lemma}
\label{lem:extcase3}
For a dual-tree algorithm with $S_q \sim S_r \sim O(N)$ using cover trees and
the traversal given in Algorithm \ref{alg:cover-tree-dual}, the number of extra
reference recursions that happen after the last query recursion is bounded by

@@

\begin{thm}
\label{thm:ct-runtime}
%For any dual-tree algorithm using cover trees and the standard cover tree
%dual-tree pruning traversal (Algorithm \ref{alg:cover-tree-dual}) with reference
%set $S_r$ that has expansion constant $c_r$ and query set $S_q$, the runtime is
%bounded above by $O(c_r^4 | R^* | \nu \chi \psi N)$, where $ | R^* | $ is
%the maximum size of the reference set $R$ (line
%\ref{alg:line:ct-dual-input}) at any point in the dual-tree pruning traversal,
%$\chi$ is the longest possible running time of \texttt{BaseCase()}, and $\psi$
%is the longest possible running time of \texttt{Score()}.
Given a reference set $S_r$ of size $N$ with an expansion constant $c_r$ and a
set of queries $S_q$ of size $O(N)$, a standard cover tree based dual-tree
algorithm (Algorithm \ref{alg:cover-tree-dual}) takes

>>>>

\begin{lemma}
\label{lem:extcase1}
For a dual-tree algorithm with $|S_q| \sim |S_r| \sim O(N)$ using cover trees and
the traversal given in Algorithm \ref{alg:cover-tree-dual}, the number of extra
reference recursions that happen before the first query recursion is bounded by

@@

\begin{lemma}
\label{lem:extcase3}
For a dual-tree algorithm with $|S_q| \sim |S_r| \sim O(N)$ using cover trees and
the traversal given in Algorithm \ref{alg:cover-tree-dual}, the number of extra
reference recursions that happen after the last query recursion is bounded by

@@

\begin{thm}
\label{thm:ct-runtime}
%For any dual-tree algorithm using cover trees and the standard cover tree
%dual-tree pruning traversal (Algorithm \ref{alg:cover-tree-dual}) with reference
%set $S_r$ that has expansion constant $c_r$ and query set $S_q$, the runtime is
%bounded above by $O(c_r^4 | R^* | \nu \chi \psi N)$, where $ | R^* | $ is
%the maximum size of the reference set $R$ (line
%\ref{alg:line:ct-dual-input}) at any point in the dual-tree pruning traversal,
%$\chi$ is the longest possible running time of \texttt{BaseCase()}, and $\psi$
%is the longest possible running time of \texttt{Score()}.
Given a reference set $S_r$ of size $O(N)$ with an expansion constant $c_r$ and a
set of queries $S_q$ of size $O(N)$, a standard cover tree based dual-tree
algorithm (Algorithm \ref{alg:cover-tree-dual}) takes

### 2015-08-14 bounds-files/sec03-approx-kde.tex
Refactor for similar notation in theorem/lemma statements.

\begin{thm}
Assume that $\mathcal{K}(\cdot, \cdot)$ is a kernel satisfying the assumptions
of the previous subsection.  Then, given a query set $S_q$ and a reference set
$S_r$ with expansion constant $c_r$, and using the approximate kernel density
estimation \texttt{BaseCase()} and \texttt{Score()} as given in Algorithms
\ref{alg:kde_base_case} and \ref{alg:kde_score}, respectively, with the
traversal given in Algorithm \ref{alg:cover-tree-dual}, the running time of
approximate kernel density estimation for some error parameter $\epsilon$ is
bounded by
%\begin{equation}
$O(c_r^{8 + \lceil \log_2 \zeta \rceil} (N + I_t(\mathscr{T}_q) + \theta))$
%\end{equation}
with $\zeta = -\mathcal{K}'(h) \mathcal{K}^{-1}(\epsilon) \epsilon^{-1}$,
$I_t(\mathscr{T}_q)$ defined as in Definition \ref{def:imbalance}, and $\theta$
defined as in Lemma \ref{lem:extcase3}.

>>>>

\begin{thm}
Assume that $\mathcal{K}(\cdot, \cdot)$ is a kernel satisfying the assumptions
of the previous subsection.  Then, given a query set $S_q$ of size $O(N)$ and a
reference set $S_r$ of size $O(N)$ with expansion constant $c_r$, and using the
approximate kernel density estimation \texttt{BaseCase()} and \texttt{Score()}
as given in Algorithms \ref{alg:kde_base_case} and \ref{alg:kde_score},
respectively, with the traversal given in Algorithm \ref{alg:cover-tree-dual},
the running time of approximate kernel density estimation for some error
parameter $\epsilon$ is bounded by
%\begin{equation}
$O(c_r^{8 + \lceil \log_2 \zeta \rceil} (N + I_t(\mathscr{T}_q) + \theta))$
%\end{equation}
with $\zeta = -\mathcal{K}'(h) \mathcal{K}^{-1}(\epsilon) \epsilon^{-1}$,
$I_t(\mathscr{T}_q)$ defined as in Definition \ref{def:imbalance}, and $\theta$
defined as in Lemma \ref{lem:extcase3}.

### 2015-08-14 bounds-files/sec04-range-search.tex
Refactor for similar notation in theorem/lemma statements.

\begin{thm}
Given a reference set $S_r$ of size $N$ with expansion constant $c_r$, and a
query set $S_q$ of size $O(N)$, a search range of $[l, u]$, and using the range
search \texttt{BaseCase()} and \texttt{Score()} as given in Algorithms
\ref{alg:rs_bc} and \ref{alg:rs_sc}, respectively, with the standard cover tree
pruning dual-tree traversal as given in Algorithm \ref{alg:cover-tree-dual}, and
also assuming that for some $\alpha > 0$,

>>>>

\begin{thm}
Given a reference set $S_r$ of size $O(N)$ with expansion constant $c_r$, and a
query set $S_q$ of size $O(N)$, a search range of $[l, u]$, and using the range
search \texttt{BaseCase()} and \texttt{Score()} as given in Algorithms
\ref{alg:rs_bc} and \ref{alg:rs_sc}, respectively, with the standard cover tree
pruning dual-tree traversal as given in Algorithm \ref{alg:cover-tree-dual}, and
also assuming that for some $\alpha > 0$,
